---
title: "0012 Code"
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: inline
---

# Load packages
```{r}
library(tmap)
library(sf)
library(spdep)
library(ggplot2)
library(deldir)
library(sp)
library(purrr)
library(here)
library(tidyverse)
library(janitor)
```



# Load data
```{r}
clev.points <- st_read(here::here("regression2.5.json"))%>%
  st_transform(.,27700)

a <- read.csv("regression2.5.csv")
```

```{r}
vehicle.points = st_as_sf(a, coords = c("lon", "lat"), crs = 4326, agr = "constant")
class(vehicle.points)

```
```{r}
plot(clev.points)
```


# Visualisation data

```{r}
LondonBoroughs <- st_read(here::here("shenzhen",
                                     "Shenzhen.shp"))%>%
  st_transform(.,27700)
qtm(LondonBoroughs) 

tmap_mode("view")
tm_shape(LondonBoroughs) +
  tm_polygons(col = NA, alpha = 0.5) +
  tm_shape(vehicle.points) +
  tm_dots(col = "blue")
```

# Spatial weight matrix
## Voronoi diagram
```{r}

vtess <- deldir(a$lon, a$lat)
plot(vtess, wlines="tess", wpoints="none",
     lty=1)

voronoipolygons = function(thiess) {
  w = tile.list(thiess)
  polys = vector(mode='list', length=length(w))
  for (i in seq(along=polys)) {
    pcrds = cbind(w[[i]]$x, w[[i]]$y)
    pcrds = rbind(pcrds, pcrds[1,])
    polys[[i]] = Polygons(list(Polygon(pcrds)), ID=as.character(i))
  }
  SP = SpatialPolygons(polys)
  voronoi = SpatialPolygonsDataFrame(SP, data=data.frame(dummy = seq(length(SP)), row.names=sapply(slot(SP, 'polygons'), 
                                                                                                   function(x) slot(x, 'ID'))))
}

v <- voronoipolygons(vtess)
plot(v)

vtess.sf <- st_as_sf(v)
plot(vtess.sf$geometry)
```



## Saptial weight matrix (queen)
```{r}

st_queen <- function(a, b = a) st_relate(a, b, pattern = "F***T****")

queen.sgbp <- st_queen(vtess.sf)

as.nb.sgbp <- function(x, ...) {
  attrs <- attributes(x)
  x <- lapply(x, function(i) { if(length(i) == 0L) 0L else i } )
  attributes(x) <- attrs
  class(x) <- "nb"
  x
}

queen.nb <- as.nb.sgbp(queen.sgbp)
queen.weights <- nb2listw(queen.nb)
queen.weights
```

## queen.nb
```{r}
queen.nb.card <- card(queen.nb)
ggplot() +
  geom_histogram(aes(x=queen.nb.card)) +
  xlab("Number of Neighbors")

summary(queen.nb)
plot(queen.nb,coords, lwd=.2, col="blue", cex = .5)
```


# Moran's I
## Moran scatter plot
```{r}

moran <- moran(a$price, queen.weights, length(queen.nb), Szero(queen.weights))
moran$I
```


## Moran's I
```{r}
EduMoran <- a %>%
  dplyr::select(price)%>%
  pull()%>%
  moran.test(., queen.weights)
EduMoran
```


## Geary's C
```{r}
EduGeary <- a %>%
  dplyr::select(price)%>%
  pull()%>%
  geary.test(., queen.weights)
```

```{r}
EduGeary
```

## local Moran's I
```{r}
Edulocalmoran <- a %>%
  dplyr::select(price)%>%
  pull()%>%
  localmoran(., queen.weights)%>%
  as_tibble()
```


```{r}
Edulocalmoran
```


## Multiple Linear regression
```{r}

Regressiondata<- a%>%
  clean_names()%>%
  dplyr::select(price, 
                lon,
                lat,
                floor_area,
                number_floors,
                room_number,
                number_bathroom,
                school_district,
                rate,
                distance_metro,
                distance_hospital,
                distance_sea)
```


## model1
```{r}
model1 <- Regressiondata %>%
  lm(price^0.75~
       lon+
       lat+
       floor_area+
       number_floors+
       room_number +
       number_bathroom+
       school_district+
       rate+
       distance_metro+
       distance_hospital+
       distance_sea,
     data=.)

```


```{r}
summary(model1)
```

# Regression model 2
```{r}
model2 <- Regressiondata %>%
  lm(price^0.75~
       lon+
       lat+
       floor_area+
       number_floors+
       number_bathroom+
       school_district+
       rate+
       distance_hospital,
     data=.)
summary(model2)
```

## Regression model 2 AIC
```{r}
AIC(model2)
```


## VIF test
```{r}
# vif test
vif(model2)
```


## print some model diagnositcs.
```{r}
par(mfrow=c(2,2))
plot(model2)
```


## Durbin-Watson test
```{r}
DW <- durbinWatsonTest(model2)
tidy(DW)
```

## write residuals out
```{r}
model_data1 <- model2 %>%
  augment(., Regressiondata)
```




# Add them to the shapelayer
```{r}
Houseprice <- clev.points %>%
  mutate(model1resids = residuals(model2))
```



# Spatial autocorrelation
# Lagrange Multiplier Diagnostics
```{r}
lm.LMtests(model2,queen.weights, zero.policy=NULL, test="all", spChk=NULL, naSubset=TRUE)
```


## residual moran's I
```{r}
Nearest_neighbour <- Houseprice %>%
  st_drop_geometry()%>%
  dplyr::select(model1resids)%>%
  pull()%>%
  moran.test(., queen.weights)%>%
  tidy()

Nearest_neighbour
```




## spatially lagged model
```{r}
SLM <- lagsarlm(price^0.75~
                                  lon+
                                  lat+
                                  floor_area+
                                  number_floors+
                                  number_bathroom+
                                  school_district+
                                  rate+
                                  distance_hospital,
                                data=Houseprice, 
                                nb2listw(queen.nb, 
                                         style="C"), 
                                method = "eigen")

summary(SLM)
```


### write out the residuals
```{r}
Houseprice <- Houseprice %>%
  mutate(slag_dv_model2_resids = residuals(SLM))

KNN4Moran <- Houseprice %>%
  st_drop_geometry()%>%
  dplyr::select(slag_dv_model2_resids)%>%
  pull()%>%
  moran.test(., queen.weights)%>%
  tidy()
KNN4Moran
```



## spatial error model
```{r}
sem_model1 <- errorsarlm(price^0.75~
                           lon+
                           lat+
                           floor_area+
                           number_floors+
                           number_bathroom+
                           school_district+
                           rate+
                           distance_hospital,
                         data=Houseprice,
                         nb2listw(queen.nb, style="C"), 
                         method = "eigen")

tidy(sem_model1)
summary(sem_model1)
```


```{r}
Houseprice <- Houseprice %>%
  mutate(sem_model1 = residuals(sem_model1))

KNN4Moranerr <- Houseprice %>%
  st_drop_geometry()%>%
  dplyr::select(sem_model1)%>%
  pull()%>%
  moran.test(., queen.weights)%>%
  tidy()
KNN4Moranerr
```


# GWR
```{r}
st_crs(Houseprice) = 27700

TrafficaccidentnumberSP <- Houseprice %>%
  as(., "Spatial")
```

## calculate kernel bandwidth
```{r}
GWRbandwidth <- gwr.sel(price^0.75~
                          lon+
                          lat+
                          floor_area+
                          number_floors+
                          number_bathroom+
                          school_district+
                          rate+
                          distance_hospital,
                        data = Houseprice, 
                        coords=cbind(a$lon,a$lat),
                        adapt=T)
GWRbandwidth
```

## run the gwr model
```{r}
gwr.model = gwr(price^0.75~
                  lon+
                  lat+
                  floor_area+
                  number_floors+
                  number_bathroom+
                  school_district+
                  rate+
                  distance_hospital,
                data = Houseprice, 
                coords=cbind(a$lon,a$lat), 
                adapt=GWRbandwidth, 
                hatmatrix=TRUE, 
                se.fit=TRUE)
gwr.model
```




